### 2024-09-26 AISTAT25/aistats.tex
Experimental section

@@

\begin{figure}
\begin{center}
  \includegraphics[width=2.5in]{figures/Monotone.png}
%\hspace{.5in}
\includegraphics[width=2.5in]{figures/Massart.png}
\end{center}
\caption{(a) The conditional probability function $\eta$ is monotonically increasing; $\eta(x) = -\gamma, 0, \gamma$ at $x = \lambda_L, \lambda, \lambda_R$, respectively. (b) On each subinterval, $\eta$ is either $> \gamma$ or $<-\gamma$.}
\label{fig:oned}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3in]{figures/MassartExperiment5.png}
\end{center}
\caption{{\bf Experimental evidence:} This figure compares the
  performance of passive sampling alone to that of the active learning
  algorithm. The X axis corresponds to the number of queries made and the
  Y axis represents the difference between the error achieved and the
  optimal achievable error.}
\label{fig:Experiments}
\end{figure}

@@

In this section we provide experimental evidence that our algorithm has low query complexity.
We chose a simple 1D problem, described in figure~\ref{fig:oned}(b)
(Massard Noise).  Although this problem is simple, it is outside the
scope of algorithms that assume that the conditional probability is a
smooth function of $x$. We used a sample of 10,000 points and ran our
algorithm 20 times. In figure~\ref{fig:experiments} we present the
average error as a function of the number of queries. We compare the
performance of our active algorithm (red line) and the performance of the passive algorithm which is the
same algorithm where focused queries are disabled and only backgroud samples are used (blue line).

Number of queries as a function of the accuracy for passive and active algorithms.
\begin{tabular}{|c|rr|c|}
\hline
err-opt &  Active&  Passive \\
\hline
0.02  &    320 &     517 \\
0.01 &     429 &    1035 \\
0.005 &678 &    2045 & \\
\hline
\end{tabular}

>>>>

The rest of the paper is organized as follows. xxxxxxx

@@

\begin{figure}[t]
\begin{center}
  \includegraphics[width=2.5in]{figures/Monotone.png}
%\hspace{.5in}
\includegraphics[width=2.5in]{figures/Massart.png}
\end{center}
\caption{(a) The conditional probability function $\eta$ is monotonically increasing; $\eta(x) = -\gamma, 0, \gamma$ at $x = \lambda_L, \lambda, \lambda_R$, respectively. (b) On each subinterval, $\eta$ is either $> \gamma$ or $<-\gamma$.}
\label{fig:oned}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3in]{figures/MassartExperiment5.png}
\end{center}
\caption{{\bf Experimental evidence:} This figure compares the
  performance of passive sampling alone to that of the active learning
  algorithm. The X axis corresponds to the number of queries made and the
  Y axis represents the difference between the error achieved and the
  Bayes error.}
\label{fig:Experiments}
\end{figure}

@@

We describe an experiment designed to evaluate our algorithm.
We use a simple 1D problem, described in figure~\ref{fig:oned}(b)
(Massard Noise).  Although this problem is simple, it is outside the scope of most non-parametric active learning algorithms, which assume smoothness of the conditional probability.

We compare two algorithms, the "active" agorithm described here, and the "passive" algorithm which uses only "background queries". We denote the difference between the error of the generated classifier and that of the Bayes optimal classifier by $\epsilon$. From the theory, we expect the query complexity of the passive algorithm to be $O(\frac{1}\epsilon})$ and of the active algorithm to be $O(\log (\frac{1}{\epsilon})$.

 For our experiment we used a sample of 10,000 unlabeled points, we repeated each of our experiments 20 times. In Figure~\ref{fig:Experiments} we show the average performance of these experiments. Note the horizontal line segments marked "active vs. passive ... ", these compare the number of queries required by the active and the passive algorithms for different accuracies
 These numbers are repeated in the following table.
\begin{tabular}{|c|rr|}
\hline
err-opt &  Active&  Passive \\
\hline
0.02  &    320 &     517 \\
0.01 &     429 &    1035 \\
0.005 &678 &    2045 \\
\hline
\end{tabular}
Considering the columns for the Active and Passive algorithms respectively, we see that the experimental query complexities concur with the theoretical predictions.
